### 2023-04-13 chapter2/chapter2.tex
Added BM analysis figures to chapter 2

>>>>

\begin{figure}[h!]
\includegraphics[width=\textwidth]{brownian/out/root.png}
\centering
\caption{\textbf{PCA of disorder regions' feature roots.}
\textbf{(A)} The first two PCs of the disorder regions' feature root distributions. The explained variance percentage of each component is indicated in parentheses in the axis labels. \textbf{(B)} The same plot as panel A with the projections of original features onto the components shown as arrows. Only the 16 features with the largest projections are shown. Scaling of the arrows is arbitrary.}
\label{fig:root}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=\textwidth]{brownian/out/rate.png}
\centering
\caption{\textbf{PCA of disorder regions' feature rates.}
\textbf{(A)} The first two PCs of the disorder regions' feature rate distributions. The explained variance percentage of each component is indicated in parentheses. \textbf{(B)} Scatter plot of the disorder regions' feature rates along the first PC against the sum of the average amino acid and indel substitution rates in those regions. \textbf{(C)} The second and third PCs of the disorder regions' feature rate distributions. The explained variance percentage of each component is indicated in parentheses in the axis labels. \textbf{(D)} The same plot as panel C with the projections of original rates onto the components shown as arrows. Only the 16 features with the largest projections are shown. Scaling of the arrows is arbitrary. \textbf{(E-F)} Example alignments of disorder regions from the orthologous groups 0A8A, 3139, 04B0, respectively. The colored bars on the left indicate the hexbin containing that region in panel C.}
\label{fig:rate}
\end{figure}
